Static Discharge of Higher-Order Interposition

### 2013-09-05 pldi2014/paper.tex
Poor use of time.

\newtheorem{thm}{Theorem}

@@

This is the grammar for chapcalc0.
\begin{schemedisplay}
(grammar
  [e ((e e ...)
      (app-values e e)
      (values e ...)
      (chaperone-operator e e e)
      (impersonate-operator e e e)
      (let ([s e]) e)
      (letrec ([s e]) e)
      (λ s e)
      (if e e e)
      (or e e)
      (and e e)
      (raise)
      x
      v
      p)]
  [p (= < + - * integer? boolean? pair? null? cons car cdr null)]
  [v (n b)]
  [n (0 1 -1 2 -2 ...)]
  [b (#t #f)]
  [s (x () (x . s))])
\end{schemedisplay}

@@

\begin{schemedisplay}
(grammar
  [e ((e e ...)
      (app-values e e)
      (chaperone-operator e e)
      (impersonate-operator e e)
      (let ([s e]) e)
      (letrec ([s e]) e)
      (if e e e)
      (or e e)
      (and e e)
      (raise e)
      (handle ([x e]) e)
      (λ s e)
      x)]
  [p (= < + - * integer? boolean?)]
  [v (n b)]
  [n (0 1 -1 2 -2 ...)]
  [b (#t #f)]
  [s (x () (x . s))])
\end{schemedisplay}

>>>>

\mathchardef\mhyphen="2D
\newtheorem{thm}{Theorem}

@@

This is the grammar for chapcalc0.
\input{calc0}

programs either evaluate to a value, evaluate to an error, or diverge.
our theorem only deals with chaperones which don't affect whether the program evaluates to a value?
a program could diverge on chaperone creation (evaluating the guards) or chaperone application (applying the guards).
this is undecidable in general.
it is possible to remove a chaperone and have some programs that errored out evaluate to a value (because the guards may artificially restrict the domain or codomain of the function).
it is possible to remove a chaperone and have some programs that errored out diverge (because the error came before divergence).
if a program evaluates to a value then no chaperone errored out and no chaperone diverged.
we also are only changing chaperones that don't error in any circumstances.
therefore, if a program evaluates to a value with a given input before erasure or promotion, it will evaluate to that value after erasure or promotion.
if a program evaluates to an error with a given input, it will evaluate to an error after, since we will not erase or promote a chaperone that /could/ throw an error, for a sound analysis.
however, programs that would have diverged otherwise may evaluate to a value or an error.

$\longrightarrow$

@@
